%----------------------------------------------------------------
%	Packages and Other Document Configurations
%----------------------------------------------------------------

\documentclass[UTF8]{resume}    % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.75in,right=0.75in,bottom=0.75in]{geometry} % Document margins
\usepackage{url}

\linespread{0.9} 

\name{Lu Niu}               % Your name
%\address{(000)~$\cdot$~111~$\cdot$~1111} % Your phone number
\address{University of Science and Technology Beijing, Beijing 100083, P.R.China} % Your address
%\address{The University of Sydney, Sydney, NW, Australia} % Your secondary address (optional)

\begin{document}

\textrm{Email:} \url{LukeNiu@outlook.com} \\
\textrm{GitHubd:} \url{GitHub.com/ConAntares}

%----------------------------------------------------------------
%	Education Section
%----------------------------------------------------------------

\begin{rSection}{Education}

{\bf The University of Sydney} \hfill {\em Jul. 2019 - Present} \\[4pt]
{\color{darkgray}{LukeNiu@outlook.com}}\textit{PhD of Science in Physics}\\[4pt]
Subject: Plasmonics \\[4pt]
Thesis: Quantum Computation Logic Circuits Realization Based on Plasmon Effects. \\[4pt]
Overall GPA:  \par

{\bf University of Science and Technology Beijing} \hfill {\em Sep. 2015 - Jun. 2017} \\[4pt]
\textit{MPhil of Science in Physics}\\[4pt]
Subject: Atom and Molecular Physics \\[4pt]
Thesis: Effect of External Field on the IV Characteristics through the Molecular Nano-junction. \\[4pt]
Overall GPA: 3.2 \par

\end{rSection}

%----------------------------------------------------------------
%	Technical Experience Section
%----------------------------------------------------------------

\begin{rSection}{Expertise and Technical Strengths}
\begin{tabular}{@{}>{\bfseries}l@{\hspace{12ex}}l}
Programming: & C/C++, Fortran, Python, Julia, \LaTeX; \\[4pt]
Software: & Linux, Git, TensorFlow, VASP, Octopus; \\[4pt]
Expertise: & Mathematical Analysis, Topology, Algorithms, Machine Learning, \\
& Density Functional Theory, Plasmonics, \\
& Quantum Optics, Quantum Computation. \\[4pt]
Language: & Chinese(Standard Mandarin), English;
\end{tabular}
\end{rSection}

%----------------------------------------------------------------
%	Research Experience Section
%----------------------------------------------------------------

\begin{rSection}{Research Experience}
    
    \begin{rSubsection}{Effect of External Field on the IV Characteristics through the Molecular Nano-junction\\}{\em Sep. 2016 - Jun. 2017}{Student}{USTB, Beijing, P.R.China}
    \item Referred to materials about molecule; analyzed steady current of two electrodes under distinct bias voltages; studied transient current under Gaussian pulse with different widths;
    \item Established the physical model of Molecular junction with external field which could produce coupling with the molecule;
    \item Simulated the physical model and conducted scientific calculation with Fortran;
    \item Visualized the result with Python; compared I-V characteristic curve of the molecular junction impacted by external field with the curve without influence from external field; 
    \item Drew the conclusion that external light field may impose effective influence on the molecular junction.
    \end{rSubsection}
        
    \begin{rSubsection}{Plasmon Enhanced Heterogeneous Electron Transfer with Continuous Band Energy Model\\}{\em Apr. 2016 - Mar. 2017}{Student}{USTB, Beijing, P.R.China}
    \item Calculated Plasmon enhanced heterogeneous electron transfer in semiconductor continuous model with master equation;
    \item Simulated the physical model and conducted scientific calculation with Fortran and Visualized;
    \item Visualized the result with Origin.
    \end{rSubsection}
        
    \begin{rSubsection}{Molecular Emission Spectrum of Combined System and its Fourier Analysis\\}{\em Dec. 2015 - Apr. 2016}{Student}{USTB, Beijing, P.R.China}
    \item Consulted related materials; probed into emission spectrum of molecular with Fourier analysis;
    \item Built the equations set which describes the physical process of the molecule system excitation in the quantization radiation field;
    \item Solved the equations with Fortran.
    \end{rSubsection}
       
    \end{rSection}
    
%----------------------------------------------------------------
%	Internship Experience Section
%----------------------------------------------------------------

\begin{rSection}{Internship Experience}

    \begin{rSubsection}{Analytical Mechanics}{\em Spring, 2017 and Spring, 2016}{Teaching Assistant}{Professor Luxia Wang}
    \item Organized exercise class; answered students' questions;
    \item Corrected assignments and papers;
    \item Helped teacher prepare course related materials.
    \end{rSubsection}

    \begin{rSubsection}{College Physics}{\em Autumn, 2016 and Autumn, 2015}{Teaching Assistant}{Lecturer Quanshui Li}
    \item Corrected assignments and papers;
    \item Answered students' questions after class.
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------
%   Published Research Articles
%----------------------------------------------------------------

\begin{rSection}{Published Research Articles}

\begin{rSubsection}{\em{2018}}{}{}{}
\item Lu Niu, Luxia Wang*; 
\em Effect of External Field on the I-V Characteristics through the Molecular Nano-junction \em (in Chinese); 
Acta Physica Sinica, 67, 027304 (2018).
\end{rSubsection}

\begin{rSubsection}{\em{2017}}{}{}{}
\item Dandan Zhao, Lu Niu, Luxia Wang*; 
\em Plasmon Enhanced Heterogeneous Electron Transfer with Continuous Band Energy Model \em ;
Chemical Physics, 493 (2017) 194-199. 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------
%   Awards and Honors
%----------------------------------------------------------------

\begin{rSection}{Awards and Honors}

\begin{tabular}{ @ {} >{\em}l @{\hspace{6ex}} l }
2015 & Third-Class Scholarship, University of Science and Technology Beijing\\
%2011 & Attendee, Capital University Students Sports Meeting, Beijing \\
%2010 & Third-class Scholarship, Beijing Information Science and Technology University\\
\end{tabular}
    
\end{rSection}

%----------------------------------------------------------------
%	Example Section
%----------------------------------------------------------------

%\begin{rSection}{Section Name}
%Section content\ldots
%\end{rSection}

%----------------------------------------------------------------

\end{document}
